Bioverse: Origins of Life

### 2024-07-11 src/tex/ms.tex
update conclusions

\section{Conclusions and future work}
We have investigated the potential of upcoming exoplanet surveys to test the hypothesis that a minimum past \gls{NUV} flux is required for abiogenesis.
To this end, we first employed a semi-analytical Bayesian analysis to estimate probabilities of obtaining strong evidence for or against this hypothesis.
We then used the Bioverse framework to assess the diagnostic power of realistic transit surveys, taking into account exoplanet demographics, time-dependency of habitability and \gls{NUV} fluxes, observational biases, and target selection.

Our main findings are:
\begin{enumerate}
    \item The required \gls{NUV} radiation in the cyanosulfidic scenario should lead to a correlation between past \gls{NUV} flux and current occurrence of biosignatures that will be observationally testable.
    \item The required sample size for detecting this correlation depends on the occurrence of life on temperate exoplanets and the distribution of host star spectral types in the sample; in particular their past maximum \gls{NUV} fluxes.
%        A direct imaging mission with the \gls{HWO} will require characterizing XXX planets ...
    \item If the predicted \gls{NUV} correlation exists, yielding strong evidence for it is likely ($> \SI{90}{\percent}$) for sample sizes $\geq 100$, and a survey strategy that targets extreme values of inferred past \gls{NUV} irradiation.
    \item Abiogenesis in the cyanosulfidic scenario prefers late host star spectral types due to the higher \gls{NUV} fluxes in their habitable zones. However, due to a wider distribution of maximum past \gls{NUV} fluxes in the \gls{HZ} of FGK stars, a transit survey targeting FGK systems is more likely to obtain strong evidence for or against the \gls{NUV} hypothesis.

>>>>

\section{Conclusions and future work}
We have investigated the potential of upcoming exoplanet surveys to test the hypothesis -- motivated by the cyanosulfidic origins-of-life scenario -- that a minimum past \gls{NUV} flux is required for abiogenesis.
To this end, we first employed a semi-analytical Bayesian analysis to estimate probabilities of obtaining strong evidence for or against this hypothesis.
We then used the Bioverse framework to assess the diagnostic power of realistic transit surveys, taking into account exoplanet demographics, time-dependency of habitability and \gls{NUV} fluxes, observational biases, and target selection.

Our main findings are:
\begin{enumerate}
    \item Under the \gls{NUV} hypothesis, the fraction of inhabited planets in a transit survey is sensitive to the threshold \gls{NUV} flux and is expected to drop sharply for required fluxes above a few hundred~\SI{}{\erg\per\second\per\centi\meter\squared}.
    \item The \gls{NUV} hypothesis should lead to a correlation between past \gls{NUV} flux and current occurrence of biosignatures that may be observationally testable.
    \item The required sample size for detecting this correlation depends on the abiogenesis rate on temperate exoplanets and the distribution of host star spectral types in the sample; in particular their past maximum \gls{NUV} fluxes.
%        A direct imaging mission with the \gls{HWO} will require characterizing XXX planets ...
    \item If the predicted \gls{NUV} correlation exists, obtaining strong evidence for the hypothesis is likely ($\gtrsim \SI{80}{\percent}$) for sample sizes $\geq 100$ if the abiogenesis rate is high ($\gtrsim \SI{50}{\percent}$) and if no very high \gls{NUV} fluxes are required.
    A survey strategy that targets extreme values of inferred past \gls{NUV} irradiation increases the diagnostic power.
    \item Samples of planets orbiting M~dwarfs overall yield higher chances of successfully testing the \gls{NUV} hypothesis and are more likely to yield biosignature detections under this hypothesis.
%    \item Abiogenesis in the cyanosulfidic scenario prefers late host star spectral types due to the higher \gls{NUV} fluxes in their habitable zones. However, due to a wider distribution of maximum past \gls{NUV} fluxes in the \gls{HZ} of FGK stars, a transit survey targeting FGK systems is more likely to obtain strong evidence for or against the \gls{NUV} hypothesis.
